Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-10-22 reviews.Rmd
add link to preprint and osf

@@

# Reviewer 1: Daniel Lakens
We begin with a summarizing our understanding of Daniel Lakens philosophical position, his main points of criticisim and our general take on how to address these issues.
Thereafter, we will provide point-by-point responses in the usual style of response letters.
Lakens and our own positions on preregistration fundamentally differ.
They each build upon two long standing traditions in philosophy of science, namely _inductionist_ and _anti-inductionist_, which differ in their core epistemological assumptions.
We believe that a lot of seemingly critical points raised by Daniel Lakens can simply be traced back to differences in these philosophical stances and thus cannot be resolved in the various sub points he raised.

>>>>

We have updated the preprint:

<https://osf.io/preprints/psyarxiv/cs8wb>

 OSF (<https://osf.io/nc5g8/>) and Zenodo (<https://doi.org/10.5281/zenodo.7648471>) are mirroring our GitHub repo (<https://github.com/aaronpeikert/bayes-prereg>).

@@

# Reviewer 1: Daniel Lakens

We begin with a summarizing our understanding of Daniel Lakens philosophical position, his main points of criticisim and our general take on how to address these issues.
Thereafter, we will provide point-by-point responses in the usual style of response letters.
Lakens and our own positions on preregistration fundamentally differ.
They each build upon two long standing traditions in philosophy of science, namely _inductionist_ and _anti-inductionist_, which differ in their core epistemological assumptions.
We believe that a lot of seemingly critical points raised by Daniel Lakens can simply be traced back to differences in these philosophical stances and thus cannot be resolved in the various sub points he raised.
